---
title: "Campaign donations from the Federal Election Commission"
author: "Eva Gjekmarkaj, Ben Baumer"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## FEC 

This is a vignette on how to use the FEC package and conduct analysis for questions such as contributions by individuals/special interests for any given election year. Below I will use the 2014 data to address the following questions:
  
  1. How much money did each State raise?

  2. How much money in aggregate did both parties raise in the 2014 midterm election?
  
  3. How much money was contributed from people to pacs for each committee?

## Connect to a local or remote database 

```{r message=FALSE}
library(fec)
db <- src_mysql_cnf(dbname = "fec")
fec <- etl("fec", db = db, dir = "~/dumps/fec")
fec
```


## ETL

  - Doing it all at once
```{r message=FALSE, eval=FALSE, warning=FALSE}
fec %>%
  etl_create(years = 2014)
```

- Note: For more information on [how the ETL Framework works](https://github.com/beanumber/etl)

### How much money did the residents of each state contribute?

```{r, eval=FALSE}
fec %>%
  tbl("individuals") %>%
  group_by(state) %>%
  summarise(Total = sum(transaction_amt)) %>%
  arrange(desc(Total))
```

- Note: There were an additional 8 classifications under the 'state' column. 

### How much money in aggregate did political parties raise the 2016 presidential election?

```{r, eval=FALSE}
committees <- fec %>% tbl("committees")
individuals <- fec %>% tbl("individuals")

committees %>%
  inner_join(individuals, by = "cmte_id") %>%
  group_by(cmte_party_affiliation) %>%
  summarise(Total = sum(transaction_amt, na.rm = TRUE))
```

3. How much money was contributed from people to pacs for each committee?

```{r eval=FALSE, results="hide"}
fec %>%
  tbl("people_to_pacs") %>%
  select(party,cmte_name, as.double(total_raised))
```
